A Test of the Frequency Independence Assumption of the Power System Parameters used in Geomagnetically Induced Current Calculations

### 2019-02-23 paper.tex
Updates from Overleaf

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_options_comparison_a.pdf}
\caption{The lower group of lines represents the estimate of $a(\omega)$ made using different pre-processing or regression methods. The upper group of lines has been shifted upwards by a factor of 10 and represents estimates made using different averaging methods. The 1 standard error error bars are only shown for the lines associated with the method used in the body of the text (labeled as ``Default'').}
\label{a_variations}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_options_comparison_a.pdf}
\caption{The lower group of lines represents the estimate of $a(\omega)$ made using different pre-processing or regression methods. The upper group of lines has been shifted upwards by a factor of 10 and represents estimates made using different averaging methods. The 1 standard error error bars are only shown for the lines associated with the method used in the body of the text (labeled as ``Default'').}
\label{b_variations}
\end{figure}

>>>>

\begin{figure}[h]
\begin{minipage}[t]{.48\linewidth}
\includegraphics[width=\textwidth]{figures/plot_options_comparison_a.pdf}
\label{plot_options_comparison_a}
\end{minipage}
\begin{minipage}[t]{.48\linewidth}
\includegraphics[width=\textwidth]{figures/plot_options_comparison_b.pdf}
\end{minipage}
\begin{minipage}[t]{.48\linewidth}
\includegraphics[width=\textwidth]{figures/plot_options_comparison_zx.pdf}
\label{plot_options_comparison_a}
\end{minipage}
\begin{minipage}[t]{.48\linewidth}
\includegraphics[width=\textwidth]{figures/plot_options_comparison_zy.pdf}
\end{minipage}

\end{figure}
